\bf Focusing on Fast Neural Network Inference

### 2018-05-17 wnmt.2018/wnmt.tex
cast

Our second system uses multiplicative-LSTM in the encoder and the first layer of a decder, and a GRU in the second layer, using an extension of the Nematus toolkit which supports such model. We trained 2 systems with differing vocabulary sizes and varied the beam sizes before choosing the the settings that produces good translation quality on the validation set, Table~\ref{tab:mLSTM BLEU - vocab sizes}.

@@

We are also working to make deep-learning faster using more specialised hardware such as FPGAs. It would be interesting as future work to bring our focused approach to fast deep-learning inference to a more general training toolkit.

>>>>

Our second system uses multiplicative-LSTM in the encoder and the first layer of a decder, and a GRU in the second layer, using an extension of the Nematus~\citep{sennrich-EtAl:2017:EACLDemo} toolkit which supports such models. We trained 2 systems with differing vocabulary sizes and varied the beam sizes before choosing the the settings that produces good translation quality on the validation set, Table~\ref{tab:mLSTM BLEU - vocab sizes}.

@@

We are also working to make deep-learning faster using more specialised hardware such as FPGAs. It would be interesting as future work to bring our focused approach to fast deep-learning inference to a more general toolkit.
